Network Cascades

### 2016-08-22 paper/paper.tex
Finish the example in the model section

@@

$
f(\phi) =
  \begin{cases}
    0 & \phi \in {0, 1} \\
    0.1 & \phi \in {0.1, 0.2, 0.3, 0.4, 0.7, 0.8, 0.9} \\
    0.2 & \phi in {0.5}
  \end{cases}
$

@@

>>>>

%TODO: Image

@@

$
f(\phi) =
  \begin{cases}
    0 & \phi \in \{0, 1\} \\
    0.1 & \phi \in \{0.1, 0.2, 0.3, 0.4, 0.7, 0.8, 0.9\} \\
    0.2 & \phi \in \{0.5\}
  \end{cases}
$

@@

In the example with Alice and the others, we apply the first propability distribution from above. Let's say that Alice and Bob are assigned a threshold of $\phi_{Alice} = \phi_{Bob} = 0.5$ (for which the propability is $20\%$), Charly is assigned $\phi_{Charly} = 0.3$ and Dave $\phi_{Dave} = 0.9$. This means that Dave is very hard to ``convince'', at least $90\%$ of his neighbors must use WhatsApp before he decides to use it (switch his state to $1$), whereas Charly already switches if only $30\%$ of his neighbors adopt the technology. Since Dave has only 1 neighbor, Charly, he switches as soon as Charly switches (in this case, $100\%$ of his neighbors would have switched). Dave has two neighbors, Bob and Dave, but only needs $30\%$ to switch, so it suffices if either Bob or Dave switch (that would be $50\%$ of his neighbors).
